---
title: "Exercises"
output:
  rmarkdown::html_document
---

# Introduction

Please install the packages:

- ggplot2
- tufte

## Task 1

Write a "question" that tests if `a` is equal to `b`:

```{r}
a <- 3
b <- 4

# your code here
a == b
```

## Task 2

Write a "question" that tests which values in `a` are equal to the value "d":

```{r}
a <- c("a", "b", "c", "d", "e")

# your code here
a == "d"
```

## Task 3

Write a "question" that tests which values in `a` are equal to the value "d":

```{r}
a <- c("a", "b", "c", "d", "e")

# your code here
a == "d"
```

## Task 4

Select all rows from the data.frame diamonds with "Premium" cut

In STATA, the code would be:

browse if cut=="Premium"

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
diamonds[diamonds$cut=="Premium",]
```

## Task 5

For all rows in the data.frame diamonds, set the price to 300

In STATA, the code would be:

replace price = 300

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
diamonds$price <- 300
diamonds
```

## Task 6

For all rows in the data.frame diamonds where the cut is "Ideal" and the color is "E", set the price to 2*depth

In STATA, the code would be:

replace price = 2*depth if cut=="Ideal" & color=="E"

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
rows <- diamonds$cut=="Ideal" & diamonds$color=="E"
diamonds[rows,]$price <- 2*diamonds[rows,]$depth
diamonds
```

## Task 7

Count how many rows have a color "E"

In STATA, the code would be:

count if color=="E"

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
sum(diamonds$color=="E")
```

## Task 8

What is the mean price for diamonds with carat greater than 0.23 and color is "E", "I", or "J"?

In STATA, the code would be:

sum price if carat>0.23 & (color=="E" | color=="I" | color=="J")

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
rows <- diamonds$carat>0.23 & diamonds$color %in% c("E", "I", "J")
mean(diamonds[rows,]$price)
```

## Task 9

Set the price for all diamonds with "Good" cut to NA and then find the overall mean price

In STATA, the code would be:

replace price = . if cut=="Good"
sum price

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
diamonds[diamonds$cut=="Good",]$price <- NA
mean(diamonds$price, na.rm=T)
```

## Task 10

Within the diamonds whose cut is "Very Good", find the proportion whose price is under 340

In STATA, the code would be:

gen under340=0 if cut=="Very Good"
replace under340=1 if cut=="Very Good" & price<340
sum under340

```{r}
data("diamonds", package="ggplot2")
diamonds <- diamonds[1:20,]

# your code here
rows <- diamonds$cut=="Very Good"
mean(diamonds[rows,]$price<340)
```





