---
title: "If statements/data selection/NA"
output: rmarkdown::html_document
---

## What is TRUE or FALSE?

Today we will be working a lot with `TRUE` and `FALSE`.

Let us start off with a recap of last week. `TRUE`/`FALSE` are `boolean` variables. We can print them:

```{r}
print(TRUE)
print(FALSE)
```

We can also assign them:

```{r}
a <- TRUE
print(a)
```

```{r}
b <- FALSE
print(b)
```

We can also **CREATE** them from questions:

```{r}
print(3==4)
```

Note the use of the `==`. Double `==` is a **QUESTION**. Single `=` is an **ASSIGNMENT**.

We can also save the result of the question ("is 3 equal to 4?") in the variable `a` and then print the result:

```{r}
a <- 3==4
print(a)
```

We can also ask other questions:

```{r}
print(3!=4) # is 3 not equal to 4?
print(3<4) # is 3 less than 4?
print(3<=4) # is 3 less than or equal to 4?
print(3>4) # is 3 greater than 4?
print(3>=4) # is 3 greater than or equal to 4?
print(3 %in% c(1,2)) # is 3 equal to 1 or 2?
print(!3 %in% c(1,2)) # is 3 NOT equal to 1 or 2?
```
