---
title: "If statements/data selection/NA"
output:
  tufte::tufte_html:
    tufte_variant: envisioned
    highlight: tango
---

# Introduction

Please install the packages:

- ggplot2
- tufte

# What is TRUE/FALSE?

Today we will be working a lot with `TRUE` and `FALSE`.

Let us start off with a recap of last week. `TRUE`/`FALSE` are `boolean` variables. We can print them:

```{r}
print(TRUE)
print(FALSE)
```

We can also assign them:

```{r}
a <- TRUE
print(a)

b <- FALSE
print(b)
```

We can also **CREATE** them from questions:

`r tufte::margin_note("Note the use of == <br> Double == is a **QUESTION** <br> Single = is an **ASSIGNMENT**")`

```{r}
3==4
```

We can also save the result of the question ("is 3 equal to 4?") in the variable `a` and then print the result:

```{r}
a <- 3==4
a
```

We can also ask other questions:

`r tufte::margin_note("**!** means **NOT**")`

```{r}
3!=4 # is 3 not equal to 4?
3<4 # is 3 less than 4?
3<=4 # is 3 less than or equal to 4?
3>4 # is 3 greater than 4?
3>=4 # is 3 greater than or equal to 4?
c(1,2,3,4) == 3 # FOUR questions simultaneously
c(3,4)<c(4,1) # TWO questions simultaneously (not recommended)
```

The above questions (`==`, `!=`, `<`, `<=`, `>`, `>=`) **MUST** have either:

1. Have one single value on the right side of the question (recommended)
2. Have variables that are the same length on the left and the right of the question (not recommended)

`r tufte::margin_note("The number of questions we ask **ALWAYS** corresponds to the length of the variable on the left side of the question")`

The below questions can have different length variables on each side of the question:

```{r}
3 %in% c(1,2) # is 3 equal to 1 or 2?
!3 %in% c(1,2) # is 3 NOT equal to 1 or 2?
c(1,3) %in% c(2,3,4,5) # TWO questions simultaneously
```

`r tufte::margin_note("We do not use **c** as a variable because it is already a function")`

We can obviously repeat all of these questions using variables instead of numbers:

```{r}
a <- 3
b <- 4
x <- c(1,2)
a!=b # is 3 not equal to 4?
a<b # is 3 less than 4?
a<=b # is 3 less than or equal to 4?
a>b # is 3 greater than 4?
a>=b # is 3 greater than or equal to 4?
a %in% x # is 3 equal to 1 or 2?
!a %in% x # is 3 NOT equal to 1 or 2?
```

## Exercises

Check to see if `myAge` is greater than or equal to `ageLimitForBuyingAlcohol`:

```{r}
myAge <- 13
ageLimitForBuyingAlcohol <- 18

# your code goes here
```

Check to see if `myFriendsAges` are greater than or equal to `ageLimitForBuyingAlcohol`:

```{r}
myFriendsAges <- c(15, 16, 16, 14, 20)
ageLimitForBuyingAlcohol <- 18

# your code goes here
```

Check to see if `placeWhereILive` exists in `validCityNames`:

```{r}
placeWhereILive <- "Norway"
validCityNames <- c("Oslo", "Bergen", "Trondheim")

# your code goes here
```

Check to see if `placesWhereMyFriendsLive` are **NOT** in `placesInTheEU`:

```{r}
placesWhereMyFriendsLive <- c("Australia", "UK", "London", "Paris")
placesInTheEU <- c("France", "Paris", "Sweden")

# your code goes here
```

# AND/OR

If we have multiple questions we can join them together using `&` (AND) and `|` (OR).

```{r}
TRUE & TRUE
TRUE & FALSE
FALSE & FALSE
TRUE | TRUE
TRUE | FALSE
FALSE | FALSE
```

`r tufte::margin_note("Whenever using | and \\& it is always smart to use () to ensure your order of operations is correct")`

Put into more practical examples:

```{r}
(3<4) & (2<5)
(3<4) & (5<2)
(4<3) & (5<2)
(3<4) | (2<5)
(3<4) | (5<2)
(4<3) | (5<2)
```

# Data Selection

## Vectors 

When we want to select data, we can either provide the location of the data we want (index) or a vector of `TRUE/FALSE` that essentially specifies `include/exclude` for every datapoint.

```{r}
myData <- c("a", "b", "c", "d", "e")
myData
myData[2] # using indexes
myData[c(2,4)] # using indexes
myData[c(FALSE, TRUE, TRUE, FALSE, FALSE)] # using TRUE/FALSE
```

## data.frames

We use a data.frame provided to us by the R package `ggplot2` (you might need to install this package):

```{r}
data(diamonds, package="ggplot2")
diamonds <- diamonds[1:20,]
diamonds
```

Remember that each column of a data.frame is a vector, so we can reuse what we learnt with vectors (selecting the first three values in the vector):

```{r}
diamonds$carat[c(1:3)]
diamonds$cut[c(1:3)]
```

We can also select the first three rows of a data.frame:

`r tufte::margin_note("We reference cells in data.frames by [ROWS, COLUMNS]. So diamonds[c(1:3),] means 'first three rows, all the columns'")`

```{r}
diamonds[c(1:3),]
```

The first two rows and the second and third columns (not recommended):

```{r}
diamonds[c(1:2),c(2:3)]
```

We can also specify the columns by name (recommended):

```{r}
diamonds[c(1:2),c("cut","color")]
```

We can also use a vector of `TRUE/FALSE` instead of indexes:

```{r}
diamonds[c(TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE),c("cut","color")]
```

**Most importantly** we can select rows by asking questions:

```{r}
isCutPremium <- diamonds$cut=="Premium"
isCutPremium
diamonds[isCutPremium,]
```

And we can make this more elegant:

```{r}
diamonds[diamonds$cut=="Premium",]
```

We can also ask multiple questions:

```{r}
diamonds[diamonds$cut=="Premium" & diamonds$color=="E",]
diamonds[diamonds$cut=="Premium" | diamonds$color=="E",]
diamonds[diamonds$cut %in% c("Premium","Good") | diamonds$color=="E",]
diamonds[diamonds$cut %in% c("Premium","Good") & diamonds$price<350,]
```

Once we have selected the rows we are interested in, we can then choose columns/variables:

```{r}
diamonds[diamonds$cut=="Premium" & diamonds$color=="E",]$price
diamonds[diamonds$cut=="Premium" | diamonds$color=="E",]$price
diamonds[diamonds$cut %in% c("Premium","Good") | diamonds$color=="E",]$price
diamonds[diamonds$cut %in% c("Premium","Good") & diamonds$price<350,]$price
```

You can start to work with the data to get summary statistics:

```{r}
mean(diamonds[diamonds$cut=="Premium" & diamonds$color=="E",]$price)
sd(diamonds[diamonds$cut=="Premium" & diamonds$color=="E",]$price)
quantile(diamonds[diamonds$cut=="Premium" & diamonds$color=="E",]$price)
```

Remember that behind each of these row selections is a vector containing `TRUE`/`FALSE` that includes/excludes certain rows:

```{r}
diamonds$cut=="Premium" & diamonds$color=="E"
diamonds$cut=="Premium" | diamonds$color=="E"
diamonds$cut %in% c("Premium","Good") | diamonds$color=="E"
diamonds$cut %in% c("Premium","Good") & diamonds$price<350
```

## Data manipulation/cleaning

Once you have selected your rows, you can also manipulate your data:

```{r}
diamonds # before
diamonds[diamonds$cut=="Premium" & diamonds$color=="E",]$y <- 1000 # manipulate
diamonds # after
```

This is how we clean our data. Here we change `cut=="Premium"` to `Ideal`:

```{r}
diamonds # before
diamonds[diamonds$cut=="Premium",]$cut <- "Ideal" # manipulate
diamonds # after
```

We can also add different columns together:

```{r}
diamonds # before
diamonds[diamonds$cut=="Ideal",]$x <- diamonds[diamonds$cut=="Ideal",]$y + diamonds[diamonds$cut=="Ideal",]$z
diamonds # after
```

When we need to make multiple references to particular row selections, it is often cleaner to create a variable that contains the row selections:

```{r}
# get row selection
rows <- diamonds$cut %in% c("Ideal","Good") | diamonds$color=="E"
rows

diamonds # before
diamonds[rows,]$x <- diamonds[rows,]$y + diamonds[rows,]$z*100
diamonds # after
```

## Creating new data.frames

Once you have selected your rows, you can also save it to a new data.frame:

```{r}
myNewDataFrame <- diamonds[diamonds$cut=="Ideal" & diamonds$color=="E",]
myNewDataFrame
```

## Exercises

**Task 1:** Select all rows with:

- `colour` equals `E` or `I` AND
- `price` less than `400`

Solution 1:

```{r}
diamonds[diamonds$color %in% c("E","I") & diamonds$price<400,]
```

**Task 2:** Select all rows with:

- `depth` less than 63
- `price` more than `300`

Solution 2:

```{r}
# your code goes here
```

**Task 3:** 

Set `z` to `400` for all rows with:

- `cut` not `Ideal`
- `price` more than `300`

Solution 3:

```{r}
# your code goes here
```

# Control flow (if statements)

Today's module has so far only focused on using `TRUE`/`FALSE` to select data.

We can also use `TRUE`/`FALSE` to change the flow of the program.

```{r}
if(TRUE){
  print("a")
} else {
  print("b")
}
```

Above we have used `TRUE`/`FALSE` to select which lines of code would run. This is called an `if` statement.

These will be used more frequently in further modules, but at this stage you could use them in conjuction with `flags` at the start of your script.

```{r}
analyseCheapDiamonds <- TRUE # a flag

if(analyseCheapDiamonds){
  analysisData <- diamonds[diamonds$price<350,]
} else {
  analysisData <- diamonds
}

analysisData
```

In the above script the user can change the top line `analyseCheapDiamonds <- TRUE` to be `TRUE`/`FALSE` if they want `analysisData` to be only cheap diamonds or all of the diamonds. The rest of the script would continue using `analysisData`, which would mean that you could write 1 analysis script that could be used for 2 (or more) different datasets.

We can also write more complicated `if` statements. In the following code, the flag `analysis` can take the values: `main`, `sensitivity1`, `sensitivity2` and changes the dataset accordingly:

```{r}
analysis <- "main"

if(analysis=="main"){
  analysisData <- diamonds
} else if(analysis=="sensitivity1"){
  analysisData <- diamonds[diamonds$cut!="Good",]
} else if(analysis=="sensitivity2"){
  analysisData <- diamonds[diamonds$color=="E",]
} else {
  stop("not a valid analysis!")
}

analysisData
```

If you were running regression analyses, then you could take it even further and have different outcomes, exposures, and confounders for each analysis:

```{r}
analysis <- "main"

if(analysis=="main"){
  analysisData <- diamonds
  outcome <- "price"
  exposure <- "carat"
  confounders <- c("color","clarity","depth")
} else if(analysis=="sensitivity1"){
  analysisData <- diamonds[diamonds$cut!="Good",]
  outcome <- "price"
  exposure <- "carat"
  confounders <- c("cut","clarity")
} else if(analysis=="sensitivity2"){
  analysisData <- diamonds[diamonds$color=="E",]
  outcome <- "price"
  exposure <- "cut"
  confounders <- c("depth")
} else {
  stop("not a valid analysis!")
}

# create new data.frame
analysisData <- analysisData[,c(outcome,exposure,confounders)]
analysisData

# rename variables in the data.frame
names(analysisData)[c(1:2)] <- c("outcome","exposure")
names(analysisData)[c(3:ncol(analysisData))] <- paste0("confounder",1:length(confounders))
analysisData

# 'analyse' some of the data.frame
mean(analysisData$outcome)
mean(analysisData$exposure)
cor(analysisData$outcome,analysisData$exposure)

plot(outcome~exposure, data=analysisData)
```

# NA/Missing/Invalid Data

There are two kinds of missing/invalid data:

- What **YOU** know is missing/invalid
- What **R** knows is missing/invalid

```{r}
myWeightOverTime <- c(80, 86, 76, 80, -9, -9, -9, 0, 0, 0, 89)
myWeightOverTime
mean(myWeightOverTime)
```

Here, it is obvious to **me** that the values between 70 and 90 are valid, while `-9` and `0` are obviously missing data.

For **R** all of these values are valid and real. The **ONLY** value that **R** considers to be missing/invalid is `NA`. So we need to translate my knowledge of the data, and my understanding of what values are missing/invalid into `NA`s that R can understand:

```{r}
myWeightOverTime[(myWeightOverTime<70) | (myWeightOverTime>90)] <- NA
myWeightOverTime
```

We can now analyse the data:

```{r}
mean(myWeightOverTime)
```

This doesn't work, because there are `NA`s in the data. We need to explicitly tell R to ignore the `NA`s:

```{r}
mean(myWeightOverTime, na.rm=TRUE)
```

Of course, all of this applies to data.frames:

```{r}
diamonds # before
diamonds[diamonds$cut %in% c("Good","Fair"),]$price <- NA # manipulation
diamonds # after

mean(diamonds$price)
mean(diamonds$price, na.rm=TRUE)
```

We can now introduce the function (question) `is.na`:

```{r}
is.na(4)
is.na("hello")
is.na(NA)
```

And if we apply it to a vector that contains `NA`s:

```{r}
diamonds$price
is.na(diamonds$price)
```

So we can then use `is.na` in row selections, the same as all of the other questions (`==`, `!=`, `<`, `<=`, `>`, `>=`, `%in%`):

```{r}
diamonds[is.na(diamonds$price),]
diamonds[!is.na(diamonds$price),]
```

# Sum and Mean on TRUE/FALSE

You can use `sum` to count how many observations are true:

```{r}
sum(c(TRUE,TRUE,FALSE,FALSE,FALSE,NA),na.rm=T)
sum(diamonds$price<350,na.rm=T)
```

You can use `mean` to see the proportion of values that are true:

```{r}
mean(c(TRUE,TRUE,FALSE,FALSE,FALSE,NA),na.rm=T)
mean(diamonds$price<350,na.rm=T)
```
