---
title: "Peep Interim Analysis"
author: Richard White, PhD (Biostatistics)
date: "`r lubridate::today()`"
output:
  
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
RAWmisc::AllowFileManipulationFromInitialiseProject()
RAWmisc::InitialiseProject(
  HOME = "/git/code_major/2017/ketil_peep/",
  RAW = "/analyses/data_raw/code_major/2017/ketil_peep/",
  CLEAN = "/analyses/data_clean/code_major/2017/ketil_peep",
  BAKED = "/analyses/results_baked/code_major/2017/ketil_peep/",
  FINAL = "/analyses/results_final/code_major/2017/ketil_peep/",
  SHARED = "/dropbox/results_shared/code_major/2017/ketil_peep/")

library(data.table)
```

## Data
### Loading
```{r}
d <- haven::read_sav(file.path(RAWmisc::PROJ$RAW,"171117 INTERIM SHORT Safer Births 260916_300917.sav"))
```

### Raw data
```{r}
table(d[,c("Outcome_24hours","Resuscitator")])
```

### Cleaning
```{r}
d$Outcome_24hours <- haven::as_factor(d$Outcome_24hours)
d$Resuscitator <- haven::as_factor(d$Resuscitator)
d <- data.table(d)
d <- d[Outcome_24hours %in% c("Normal","still in neonatal unit","Death")]
```

### Numbers
```{r, warning=FALSE, results='asis'}
tab <- table(d[,c("Outcome_24hours","Resuscitator")],
             exclude=c("FSB","MSB","seizures","Standard"))
prop <- prop.table(tab, margin=2)

displayTab <- tab
for(i in 1:nrow(displayTab)) for(j in 1:ncol(displayTab)){
  displayTab[i,j] <- sprintf("%s (%s%%)",displayTab[i,j], round(prop[i,j]*100))
}
pander::pandoc.table(displayTab)
```

\newpage

## Analysis

### Fisher's Exact Test (Outcome_24hours vs Resuscitator)
```{r}
fisher.test(tab)
```

### Chi-Squared Test (Outcome_24hours vs Resuscitator)
```{r}
chisq.test(tab)
```

## Conclusion

Neither the Fisher's exact test nor the Chi-Squared test were significant at an $\alpha$=5% level when testing Outcome_24hours vs Resuscitator.

There is no evidence to warrant suspension of the trial. I therefore recommend continuing with the trial.
